---
title: "Predictive Model for YouTrend"
author: "Daivaksh Patel"
output:
  html_document: default
  pdf_document: default
---

```{r warning=FALSE}
# load necessary packages
library(tidyverse)
library(gridExtra)
library(lmtest)
```

## Gathering and cleaning/validating dataset

```{r}
# Load the 'grades.csv' data set
bra = read.csv("BR_youtube_trending_data.csv")
usa = read.csv("US_youtube_trending_data (3).csv")
can = read.csv("CA_youtube_trending_data.csv")
ind = read.csv("IN_youtube_trending_data.csv")
jpn = read.csv("JP_youtube_trending_data.csv")
```


```{r}
# Looking at the structure of the data
dim(bra)
dim(usa)
dim(can)
dim(ind)
dim(jpn)
```
```{r}
colnames(bra)
```

```{r}
str(bra)
```


```{r}
library(ggplot2)
library(dplyr)
library(lubridate)

bra$publishedAt <- as.Date(bra$publishedAt)
bra %>%
  group_by(publishedAt) %>%
  summarize(AvgViewCount = mean(view_count, na.rm = TRUE)) %>%
  ggplot(aes(x = publishedAt, y = AvgViewCount)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average View Count per Day", x = "Published Date", y = "Average View Count")

```

```{r}
bra %>%
  group_by(channelTitle) %>%
  summarize(AvgViewCount = mean(view_count, na.rm = TRUE)) %>%
  top_n(10, AvgViewCount) %>%
  ggplot(aes(x = reorder(channelTitle, AvgViewCount), y = AvgViewCount)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  coord_flip() +
  labs(title = "Top 10 Channels by Average View Count", x = "Channel Title", y = "Average View Count")

```
```{r}
bra %>%
  group_by(categoryId) %>%
  summarize(AvgViewCount = mean(view_count, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(categoryId), y = AvgViewCount)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Average View Count per Category", x = "Category ID", y = "Average View Count")
```
```{r}
ggplot(bra, aes(x = comment_count, y = view_count)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(title = "Comment Count and View Count", x = "Comment Count", y = "View Count")
```

## Understanding the full Multiple Linear Regression model

```{r}
# Merging the datasets
data <- rbind(bra, usa, can, jpn, ind)

# View the structure of the merged dataset
dim(data)
```


#### MLR model to predict final exam grades by including all prediction variables
```{r warning=FALSE}
data$countryName <- factor(data$countryName)
```


```{r warning=FALSE}
# Now create the linear model
full_model <- lm(view_count ~ likes + comment_count + countryCode, data = data)

# View the summary of the model
summary(full_model)
```

## Model Diagnostics

#### Checking whether variance assumption is met

```{r warning=FALSE}
plot(full_model, which=1)
```

#### Interpreting the coefficient of multiple determination R^2.

We can get the value of the R^2 from the summary
 
```{r}
summary(full_model)$r.squared
```

The R^2 value of 80.41% means that approximately 80.41% of the variability in view_count can be explained by the linear relationship between the response variable and the predictor variables.

```{r}
summary(full_model)$fstatistic
```



 
 
 
 
 


